\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-07-18 paper/manuscript.tex
updated the table describing filetypes
added a paragraph on the weak/strong mayor/city council issue -- to the data section -- maybe this should be in the conclusion instead

@@

\input{tables/filetypes.tex}

>>>>

One of the more subtle aspects of local government is the presence of different types of government structures. Between council-manager governments and mayor-council governments - either in the weak or strong mayor variant - there is a certain degree of variance in where a city's executive authority lies. Unfortunately we do not have access to information about the type of governments across the breadth of our dataset and therefore have to assume that the partisanship of a city's mayor corresponds to the partisanship of the entity responsible for determining the content on its website. Given the prominent place of mayors tend to have on their cities' websites, as well as the fact that council-manager city governments tend to appoint mayors rather than elect them (meaning there are unlikely to be many in our dataset), we feel that any bias arising from this nuance should be minor at the most.

@@

\input{tables/tabFiletypeFrequencies.tex}
